Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-04 paper/ms.tex
Fix reference to old lines in fig

For the medium $J_z$ orbit (orange), the situation is better, although such an
orbit is not a good fit to any of the nearby open clusters \Gus{Table x}. For
m12i and m12f, the neighborhood is $\sim \text{few}\,\kpc$ for
$m_c\sim10^2\,\Msun$. At $\sim10^3\,\Msun$ the curves reach their maximum
value. For m12m, the neighborhood starts at $\sim10\,\kpc$ and quickly rises
to the maximum value. For the high $J_z$ orbit (red), the neighborhood is at
the maximum value for nearly all masses, except at the very low-mass end in
m12i.

>>>>

For the thick orbit (brown), the neighborhood is at the maximum value for
nearly all masses, except at the very low-mass end in m12i.
